---
title: "重回帰分析"
author: "RRR"
date: "2021/11/4"
output:
  slidy_presentation: default
  ioslides_presentation: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## データの概要

### 「顧客満足度データ.csv」に含まれる変数

-   「店舗番号」：各店舗にランダムに付与されたID
-   「顧客数」：各店舗の顧客数
-   「立地満足度」：立地に関する顧客満足度の平均
-   「設備満足度」：設備に関する顧客満足度の平均
-   「店舗面積満足度」：店舗面積に関する顧客満足度の平均
-   「トレーナー満足度」：トレーナーに関する満足度の平均 
-   「トレーナー数」：各店舗のトレーナー数
-   「接客研修」：１＝研修あり、０＝なし
-   「入会特典」：１＝特典あり、０＝なし


## 分析の目的と概要

### 単回帰モデル

$$
顧客数 = \alpha + \beta × 立地満足度 + 誤差 
$$

### 重回帰モデル

$$
顧客数 = \alpha + \beta_1 × 立地満足度 + \beta_2 × 設備満足度 + 誤差 
$$


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
